Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-08 WSSSPE2_report/WSSSPE2_review.tex
small changes

Kaitlin Thaney is the Director of the Mozilla Science Lab (hereafter Mozilla).
Mozilla is a non-profit organization interested in openness, in news, in website
creation, and in Science, taking advantage of the open web.

Thaney started noting the unfortunate fact that many current systems have been designed to create friction hindering us, despite the original intentions.%---social issues hindering us
An example is the National Cancer Institute's caBIG. 
A total of $\$350m$ was spent, more than $\$60m$ for management, $70+$ tools created, but still seen
as a failure (Kaitlin didn't really say why? Were the tools used? Did they
immediately bit-rot? Was their development unsustained?)-should ask question
about this.
 Those that had the least investment were the most used, the largest
investments were the least used.
 Is there a caBIG report available? Quotes from Andrea Califano/Joe Gray,
looks like there is:
\url{http://tinyurl.com/maf6dz2}.%http://www.informationweek.com/architecture/report-blasts-problem-plagued-cancer-research-grid/d/d-id/1097068?

@@

Inefficiency: \url{http://www.xkcd.com/1445/}. Need research tools (e.g. software repositories), social capital (e.g.
incentives) and capacity (eg training and mentorship) for efficient reproducible
research.

Our systems need to talk to each other but Q for speaker is that as
systems become less monolithic, paradoxically it may be harder to sustain the
links between them see:
\url{http://tinyurl.com/l76tba2}%http://www.slideshare.net/jameshowison/scientific-software-sustainability-and-ecosystem-complexity
(but does Anon Grizzly have other cites/info for that?).
Note, for example, that creative commons licensed works typically do not 
have dependencies (a book, a photo, an artwork).
Software Discovery Index: \url{http://softwarediscoveryindex.org/report/}.

@@

\item Daniel Katz and Arfon Smith. Implementing Transitive Credit with
{JSON-LD}~\cite{wssspe2_katz}

>>>>

Kaitlin Thaney is the Director of the Mozilla Science Lab (hereafter Mozilla).
Mozilla is a non-profit organization interested in openness, in news, in website
creation, and in Science, all taking advantage of the open web.

Thaney started noting the unfortunate fact that many current systems have been designed to create friction hindering us, despite the original intentions. \katznote{prev sentence is confusing}%---social issues hindering us
An example is the National Cancer Institute's caBIG. 
A total of \$350m was spent, including more than \$60m for management.  $70+$ tools were created, but caBIG is still seen
as a failure (Kaitlin didn't really say why? Were the tools used? Did they
immediately bit-rot? Was their development unsustained?)-should ask question
about this.
 Those that had the least investment were the most used, the largest
investments were the least used.
 Is there a caBIG report available? Quotes from Andrea Califano/Joe Gray,
looks like there is:
\url{http://tinyurl.com/maf6dz2}. %http://www.informationweek.com/architecture/report-blasts-problem-plagued-cancer-research-grid/d/d-id/1097068?

@@

Inefficiency: \url{http://www.xkcd.com/1445/}. Need research tools (e.g., software repositories), social capital (e.g.,
incentives) and capacity (e.g., training and mentorship) for efficient reproducible
research.

Our systems need to talk to each other but Q for speaker is that as
systems become less monolithic, paradoxically it may be harder to sustain the
links between them see:
\url{http://tinyurl.com/l76tba2} %http://www.slideshare.net/jameshowison/scientific-software-sustainability-and-ecosystem-complexity
(but does Anon Grizzly have other cites/info for that?).
Note, for example, that creative commons licensed works typically do not 
have dependencies (a book, a photo, an artwork).
Software Discovery Index: \url{http://softwarediscoveryindex.org/report/}.

@@

\item Daniel S. Katz and Arfon M. Smith. Implementing Transitive Credit with
{JSON-LD}~\cite{wssspe2_katz}
